Testing atlantisom: generate census length comps for Northeast US Atlantis

### 2019-05-13 visualization_Rmd/NEUSTrueLengthCompTest.Rmd
testing NEUS lf

---
title: "Testing atlantisom: generate census length comps for Norwegian Barents Sea Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

First we subset the nums, resn, and structn components of `run_truth` using the same `create_survey` design selecting boxes, time (*once per year for NOBA*), and species. We need only apply survey efficiency and selectivity to nums, however (done above), so we apply `aggregateDensityData` here.

@@

Select a single species for testing. Generating length composition for a single species should take just a few minutes to run. Update: for NOBA with many output timesteps, even a single species took 15-20 minutes.

@@

ss_numsallhigh <- numsallhigh[numsallhigh$species == "Green_halibut",]
ss_structnall <- structnall[structnall$species == "Green_halibut",]
ss_resnall <- resnall[resnall$species == "Green_halibut",]

@@

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

This code block can take hours (5+ for CCA and estimated 17+ for NOBA, but it never finished after 32+) to run, so be prepared, but then the saved file can be read back in to have length comps for all surveyed species. For a normal survey query we would have only one output timestep per year, which should save some time.

And lets change NOBA to estimate length only 1 timestep per year (~2.5 hours to run):

```{r allspplength, echo=TRUE, eval=FALSE}

@@

ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Norwegian_ssh")

>>>>

---
title: "Testing atlantisom: generate census length comps for Northeast US Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

First we subset the nums, resn, and structn components of `run_truth` using the same `create_survey` design selecting boxes, time (*once per year for NEUS*), and species. We need only apply survey efficiency and selectivity to nums, however (done above), so we apply `aggregateDensityData` here.

@@

Select a single species for testing. Generating length composition for a single species should take just a few minutes to run. Update: for NOBA with many output timesteps, even a single species took 15-20 minutes, so we apply this at the annual level for NEUS.

@@

ss_numsallhigh <- numsallhigh[numsallhigh$species == "SkateRay",]
ss_structnall <- structnall[structnall$species == "SkateRay",]
ss_resnall <- resnall[resnall$species == "SkateRay",]

@@

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3, scales="free_y")
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 4, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 5, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 6, scales="free_y")
#lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 7, scales="free_y")

@@

This code block can take hours (5+ for CCA and estimated 17+ for NOBA, but it never finished after 32+) to run, so be prepared, but then the saved file can be read back in to have length comps for all surveyed species. For a normal survey query we would have only one output timestep per year, which should save some time (NOBA 2.5 hours).

For NEUS, estimate length only 1 timestep per year:

```{r allspplength, echo=TRUE}

@@

ss_length_censussurvsamp <- length_censussurvsamp$natlength %>%
  filter(species == "Planktiv_S_Fish")
